\documentclass{article}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[font=small,labelfont=bf]{subcaption}
\renewcommand{\lstlistingname}{Code}
\captionsetup[subfigure]{font=footnotesize}
\setlength{\parindent}{0in}


%% --------------------------------- %%

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{RGB}{255,255,255}
 
\lstdefinestyle{mystyle}{
	language=C++,
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\scriptsize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2, 
    frame=single  
    %rulecolor=\color{blackcolor}
}
 
\lstset{style=mystyle}

%% --------------------------------- %%


\author{Madis Ollikainen}
\title{Progress report: \\ Ensemble learning \& Euler cluster}

\begin{document}

\maketitle


\section{Setting up simulations in Euler}

Making a ensemble version of the learning schema simulations was rather easy. As the simulations are quite time consuming the logical next step seemed to be to set-up simulations in the Euler cluster. Euler has \emph{Boost} installed, it's just necessary to load the module. But neither \emph{GMP} nor \emph{MPFR} seemed to be pre-installed. Getting the code to compile took some time and googling, so just in case you haven't done it before (or I need to do it again ...) I'll document the steps I took to make our code to work (the steps necessary for the learning schema code should be the same as those necessary for the Nash eq. code). \begin{bf}WARNING: I'm no expert on these topics, so my solution might not be the optimal nor the standard one, but it seems to be a solution.\end{bf} 

\subsection{Useful websites}

\begin{itemize}
\item Euler doesn't seem to have much documentation online, but once I went over my storage limit and the administrator sent me this link to a wiki. Most of it is directly related to Brutus cluster, but it's still helpful for Euler: \\ \url{<http://brutuswiki.ethz.ch/brutus/Getting_started_with_Euler#Storage>}
\item GMP website, where to download GMP: \url{<https://gmplib.org/>}       
\item MPFR website, where to download MPFR: \url{<http://www.mpfr.org/>}
\end{itemize}

\subsection{GMP \& MPFR installation}

You have already installed both on you own computer. That was rather easy, needing just: 
\emph{configure $\rightarrow$ make $\rightarrow$ make check $\rightarrow$ make install}. Now on Euler you don't have writing permission everywhere nor is the cluster file system structured exactly the same way as a PC. Thus we can't always use the default path for the installation. Typing \emph{configure -h} gives you the list of options you can enter for \emph{configure} command (which is the command which set up you paths depending on the machine you're using). So what I did was: 

\begin{itemize}
	\item First I made a \emph{bin} directory and added directories for \emph{GMP} and \emph{MPFR} inside it. 
	\begin{itemize}
		\item[$\rightarrow$] \emph{cd }
		\item[$\rightarrow$] \emph{mkdir bin }
		\item[$\rightarrow$] \emph{mkdir bin/GMP bin/MPFR }
	\end{itemize}
	
	\item Then I installed GMP:
	\begin{itemize}
		\item[$\rightarrow$] \emph{configure \quad - -prefix=\$HOME/bin/GMP}
		\item[$\rightarrow$] \emph{make}
		\item[$\rightarrow$] \emph{make check}
		\item[$\rightarrow$] \emph{make install}
	\end{itemize}
	
	\item Finally I installed MPFR:
	\begin{itemize}
		\item[$\rightarrow$] \emph{configure \quad - -with-gmp=\$HOME/bin/GMP \quad - -prefix=\$HOME/bin/MPFR}
		\item[$\rightarrow$] \emph{make}
		\item[$\rightarrow$] \emph{make check}
		\item[$\rightarrow$] \emph{make install}
	\end{itemize}
\end{itemize}


\subsection{Compiling the code}

I added a directory called \emph{ensemble\_SML\_LFO\_EULER} into the git repository. If you upload that into Euler, it should be possible to compile the code. If you look at the \emph{makefile} you'll see that there is a bit of extra linking for the libraries, because they weren't in the default places etc. But before you can compile the code you also must load the Boost module. Typing \emph{module avail} gives you the list of modules available. Typing \emph{module load MODULE\_NAME} allows to load the module. Typing \emph{module - -help} gives you the help menu. Typing \emph{module show boost/1.55.0} gives you the information about the Boost module and its location, which is needed for the \emph{makefile} (I have already set it, but just to let you know how to find it). Now the compiling part itself is rather straight forward, you just type \emph{make} as usual.  

\subsection{Runtime linking}

Now as the libraries were not in the standard location, then it is necessary to also to make a \emph{LD\_LIBRARY\_PATH} variable for your environment, so that the program could find the library during runtime. You can put it into to your \emph{.bashrc} or \emph{.bash\_profile} file. Basically you just write down the paths to your \emph{GMP} and \emph{MPFR} libs (located inside the install directories). You'll find a copy of my \emph{.bash\_profile} file below.  

\begin{lstlisting}[
	language=bash,
	caption={My .bash\_profile file (found in the home dir in Euler)}
]
# .bash_profile

# Get the aliases and functions
if [ -f ~/.bashrc ]; then
        . ~/.bashrc
fi

# User specific environment and startup programs

PATH=$PATH:$HOME/bin:$HOME/bin/GMP/include:$HOME/bin/MPFR/include

LD_LIBRARY_PATH=$LD_LIBRARY_BATH:$HOME/bin/GMP/lib:$HOME/bin/MPFR/lib

export PATH LD_LIBRARY_PATH

\end{lstlisting}


\end{document}